A Bayesian statistical model is able to predict target-by-target selection behaviour in a human foraging task

### 2022-09-23 manuscriptRevisions.tex
would help if I saved everything
a bit more revision work

To test how well our methods generalise, we use the dataset from \citep{kristjansson2014}. We split this into a training dataset (50\% of the original data i.e. 10 trials per participant) and a test dataset (the remaining 50\% of the data). The foraging model is fit on the training dataset, and the parameters from this model are then used to predict behaviour at the level of individual trials. We show that our methods appear to generalise beyond \citep{clarke2022}: further details can be found in the \textit{Supplementary Materials: Part 2}.

@@

\begin{figure}[H]
\centering
\includegraphics[width=12 cm]{Figures/qjep_ex_paths.pdf}
\caption{(\textit{top}) Two randomly selected trials in which the model does a good job in accounting for human behaviour. Red arrows indicate places where the model prediction deviates from participant behaviour. When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation. (\textit{bottom}) Two randomly selected examples in which the model does a less good job in accounting for the order in which human participants selected the items.}
\label{fig:qjep_paths}
\end{figure}

@@

>>>>

@@

\begin{figure}[H]
\centering
\includegraphics[width=12 cm]{Figures/qjep_ex_paths.pdf}
\caption{(\textit{top}) Two randomly selected trials in which the model does a good job in accounting for human behaviour. The numbers indicate the order the participant selected targets in. Red arrows indicate places where the model prediction deviates from participant behaviour. When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation. (\textit{bottom}) Two randomly selected examples in which the model does a less good job in accounting for the order in which human participants selected the items.}
\label{fig:qjep_paths}
\end{figure}

@@

\subsection{Replication: \cite{kristjansson2014} dataset}

To test how well our methods generalise, we used the dataset from \citep{kristjansson2014}. We split this into a training dataset (50\% of the original data i.e. 10 trials per participant) and a test dataset (the remaining 50\% of the data). The foraging model is fit on the training dataset, and the parameters from this model are then used to predict behaviour at the level of individual trials. We show that our methods appear to generalise beyond \citep{clarke2022}: in particular, feature foraging was more predictable than conjunction foraging, and the model is well calibrated, with participants more frequently selecting targets with higher model assigned weights. Proximity also seems to be an important factor in determining model accuracy, at least for the feature condition, although the relatively low number of participants in this experiment makes it harder to draw strong conclusions. One interesting difference compared to \citep{clarke2022} is in initial target selection: while there was a strong bias towards starting in a corner, there was little evidence of central bias, perhaps because this experiment was completed on an iPad. Further details and graphs can be found in the \textit{Supplementary Materials: Part 2}.
